### 2012-11-08 pretextual.tex
garibadinha no esqueleto

\pretextualchapter{}
	\begin{epigrafetop}
		{from Pantheon import Obatalá\, \, \, \\
                from World import sharing, kitten \\
                \vspace{.1in}
                while True: \; \; \; \; \; \; \; \; \; \; \; \; \; \; \; \,\\
                    if sharing == 0: \; \; \; \; \;  \; \; \; \; \; \\
                        Obatalá.kill( kitten ) \; \; \;}
        {Autoria coletiva e anônima (2010)}
	\end{epigrafetop}
% \,      a small space
% \:      a medium space
% \;      a large space
% \quad   a really large space
% \qquad  a huge space
% \!      a negative space (moves things back to the left) 
%	\begin{epigrafemid}
%		{They must find it difficult ... \\ Those who have taken authority as the truth, \\ rather than truth as the authority.} %frase
%		{Gerald Massey (1828 - 1907)} %referência
%	\end{epigrafemid}
	\begin{epigrafemid}
		{If I have seen further, \\it is by standing on the shoulders of giants.} %frase
		{Sir Isaac Newton (1642 - 1727)} %referência
	\end{epigrafemid}
	\vspace{-1cm}
	\begin{epigrafebot}
		{Electronic music used pure sounds, completely calibrated. You had to think digitally, as it were, in a way that allowed you to extend serial ideas into other parameters through technology.} %frase
		{Luc Ferrari (1929 - 2005)} %referência
	\end{epigrafebot}
\resumoeabstract %Para incluir o texto do resumo e abstract,use o arquivo resumoeabstract.tex

>>>>

\pretextualchapter{}
%	\begin{epigrafetop}
%		{from Pantheon import Obatalá\, \, \, \\
%                from World import sharing, kitten \\
%                \vspace{.1in}
%                while True: \; \; \; \; \; \; \; \; \; \; \; \; \; \; \; \,\\
%                    if sharing == 0: \; \; \; \; \;  \; \; \; \; \; \\
%                        Obatalá.kill( kitten ) \; \; \;}
%        {Autoria coletiva e anônima (2010)}
%	\end{epigrafetop}

	\begin{epigrafetop}
		{Music is a hidden arithmetic exercise of the soul, which does not know that it is counting.}
        {Gottfried Leibniz (1646-1716)}
	\end{epigrafetop}

% \,      a small space
% \:      a medium space
% \;      a large space
% \quad   a really large space
% \qquad  a huge space
% \!      a negative space (moves things back to the left) 
%	\begin{epigrafemid}
%		{They must find it difficult ... \\ Those who have taken authority as the truth, \\ rather than truth as the authority.} %frase
%		{Gerald Massey (1828 - 1907)} %referência
%	\end{epigrafemid}
	\begin{epigrafemid}
		{Music is a hidden metaphysical exercise of the soul, which does not know that it is philosophizing.} %frase
		{Arthur Schopenhauer (1788-1860)} %referência
	\end{epigrafemid}
	\vspace{-1cm}
	\begin{epigrafebot}
		{Electronic music used pure sounds, completely calibrated. You had to think digitally, as it were, in a way that allowed you to extend serial ideas into other parameters through technology.} %frase
		{Luc Ferrari (1929 - 2005)} %referência
	\end{epigrafebot}
\resumoeabstract %Para incluir o texto do resumo e abstract,use o arquivo resumoeabstract.tex
